Potential Factors of Decreasing Birth Rates in the US since the Great Recession and Beyond

### 2024-02-09 outputs/paper/paper.qmd
update

>>>>

```{r}
# Load necessary libraries
library(dplyr)
library(knitr)
library(kableExtra)

# Filter the data to include years starting from 1990
filtered_data <- data %>%
  filter(year >= 1990)

# Select the required columns and rename them
selected_data <- filtered_data %>%
  select(Year = year, White = brate_whitenh, Black = brate_blacknh, Hispanic = brate_hisp)

# Print the table using additional styling
kable(selected_data, caption = "Trends in Birth Rates by Population Race and Ethnicity (ages 15-44)", format = "html") %>%
  kable_styling(full_width = FALSE) %>%
  add_header_above(c("","Births per 1,000 women" = 3))

```
